Lattice model

### 2017-04-01 oopsla17/lattice-model.tex
prop environment for proposition 1; change to isomorphic type for projections

A set of $N$-dimensional points can be \emph{projected} to the set of
1-dimensional points in the $i^{\text{th}}$ dimension by
$\pi_i : \mathcal{P}(\zinf{})^{\mkern-19mu{N}} \to
\mathcal{P}(\zinf{})$
where $i \in \mathsf{Fin}(N)$. We refer to this projected set as the
\emph{$i^{th}$ components}.
\end{defn}

\begin{proposition}
The set $\mathcal{P}{(\zinf{}^{{N}})}$ trivially forms a
  distributive lattice under the superset relation.
\end{proposition}

>>>>

A set of $N$-dimensional points can be \emph{projected} to the set of
1-dimensional points in the $i^{\text{th}}$ dimension by
$\pi_i : \mathcal{P}(\zinf{}^{\mkern0mu{N}}) \to
\mathcal{P}(\zinf{})$
where $i \in \mathsf{Fin}(N)$. We refer to this projected set as the
\emph{$i^{th}$ components}.
\end{defn}

\begin{prop}
The set $\mathcal{P}{(\zinf{}^{{N}})}$ trivially forms a
  distributive lattice under the superset relation.
\end{prop}
